Title here

### 2016-12-06 portfolio/text/ms.Rmd
Copyediting

We developed a hierarchical variance-function regression model, which separately
models changes in the mean and variance of individual revenue as a function of
covariates [@davidian1987; @hall1989]. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the variance to
be heteroscedastic and vary as a function of covariates. For application to
economic data on individual fishing portfolios, this model allows certain
strategies and levels of diversification to be more or less variable than
others. Our model includes the number of days fished to represent fishing
effort,

@@

We obtained fisheries landings and revenue data for all permit holders in Alaska
from `r range_yrs[1]` to `r range_yrs[2]` from the Alaskan Commercial Fisheries
Entry Commission (CFEC). These data represent a total of nearly `r 
round(ndat$initial_tot_rev/1e9)` billion 2009 USD and a combined `r 
round(ndat$initial/1e6,1)` million rows of data. We adjusted for inflation by
setting all revenues in 2009 USD [@bea2016]. We implemented a number of
filtering steps to focus on individuals actively engaged in commercial fishing
(Supporting Information). In particular, we removed permit holders whose median
revenue was less than \$10,000 2009 USD.

We combined similar permits into permit groupings and identified sets of permit
groupings held by an individual in a specific year as 'strategies' (Supporting
Information). For example, we combined permits that were the same except for
vessel size (e.g. a longliner fishing sablefish on a vessel under 60 ft was
considered to have the same strategy as a longliner fishing sablefish on
a vessel over 60 ft), and we combined a number of permits that were targeting
a single species and differed only in region fished. Therefore, someone fishing
herring roe in Kodiak and someone fishing herring roe in Alaska Peninsula were
both considered to have a 'herring roe' permit group. For salmon permits, we
grouped permits using the same gear type across regions for groups that shared
similar species composition. After this process of combining permits, we were
left with `r n_grouped_permits` unique fishing permit groups (Table
S\ref{tab:strategies}), which we aggregated within each person-year combination
to form permit strategies. For example, if someone fished halibut and sablefish
in the same year, their strategy for that year would be "halibut-sablefish".
Specific details on our strategy definitions are available in the Supporting
Information.

@@

The $\beta$ terms represent estimated coefficients, some of which are allowed to
vary as 'random effect' terms. The intercepts $\beta_{0,j,t}$ are allowed to
vary by strategy-year combinations, are centered on zero, and are constrained by
a normal distribution:

@@

\noindent This, combined with the lack of a global intercept, constrains the
mean change in log revenue across all fishers and years to be zero. I.e., we
assume that the data are stationary after accounting for all covariates and
including an intercept that varies with strategy-year combinations. Initial
versions of the model confirmed that the global intercept along with
stragey-level intercepts would be estimated at almost exactly zero.

@@

\noindent The $\beta_{1,j}$'s represent how much a X\% decrease in species
diversity within a strategy translates to a Y\% change in revenue. The
$\beta_{2,j}$'s represent how much an X\% increase in species diversity within
a strategy translates to a Y\% change in revenue. These are after controlling
for percent change in days fished, $\beta_3$, and the interaction between days
fished and percent change in species diversity, $\beta_4$ and $\beta_5$.

>>>>

We developed a hierarchical variance-function regression model, which separately
models changes in the mean and variance of individual revenue as a function of
covariates [@davidian1987; @hall1989]. Whereas traditional hierarchical linear
models assume homoscedasticity --- that the residual variance does not vary
systematically --- the variance-function regression model allows the variance to
be heteroscedastic and vary as a function of covariates. Our specific model
allows certain fishing strategies and levels of species diversification to
generate more or less revenue and be more or less variable than others.

@@

We obtained commercial fisheries landings and revenue data for all permit
holders in Alaska from `r range_yrs[1]` to `r range_yrs[2]` from the Alaskan
Commercial Fisheries Entry Commission (CFEC). These data represent a total of
nearly `r round(ndat$initial_tot_rev/1e9)` billion 2009 USD and a combined `r 
round(ndat$initial/1e6,1)` million rows of data. We adjusted for inflation by
setting all revenues to 2009 USD [@bea2016]. We implemented a number of
filtering steps to focus on individuals actively engaged in commercial fishing
(Supporting Information). In particular, we removed permit holders whose median
revenue was less than \$10,000 2009 USD to focus on individuals for whom
commercial fishing formed a substantial part of their income.

We combined similar permits into permit groupings and identified sets of permit
groupings held by an individual in a specific year as "strategies" (Supporting
Information). For example, we combined permits that were the same except for
vessel size (e.g. a longliner fishing sablefish on a vessel under 60 ft was
considered to have the same strategy as a longliner fishing sablefish on
a vessel over 60 ft), and we combined a number of permits that were targeting
a single species and differed only in region fished. Therefore, for example,
someone fishing herring roe in Kodiak and someone fishing herring roe in Alaska
Peninsula were both considered to have a 'herring roe' permit group. For salmon
permits, we grouped permits using the same gear type across regions for groups
that shared similar species composition. After this process of combining
permits, we were left with `r n_grouped_permits` unique fishing permit groups
(Table S\ref{tab:strategies}), which we aggregated within each person-year
combination to form permit strategies. For example, if someone fished halibut
and sablefish in the same year, their strategy for that year would be
"halibut-sablefish". Specific details on our strategy definitions are available
in the Supporting Information.

@@

The $\beta$ terms represent estimated coefficients, some of which are allowed to
vary as "random effect" terms. The intercepts $\beta_{0,j,t}$ are allowed to
vary by strategy-year combinations, are centered on zero, and are constrained by
a normal distribution:

@@

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.

@@

\noindent The $\beta_{1,j}$'s represent how much a 1\% decrease in species
diversity within a strategy translates to a Y\% change in revenue. The
$\beta_{2,j}$'s represent how much a 1\% increase in species diversity within
a strategy translates to a Y\% change in revenue. These are after controlling
for percent change in days fished, $\beta_3$, and the interaction between days
fished and percent change in species diversity, $\beta_4$ and $\beta_5$.
